\Large \bf Uncovering Distributed System Bugs during Testing (not Production!)

### 2015-08-29 methodology.tex
more text about modeling

@@

  void ProcessTickEvent()
  {
    // Nondeterministic boolean choice controlled by P#
    if (this.Nondet())
      // sends a timer tick event to the owner machine
      this.Send(this.Owner, new TimerTickEvent());
    // triggers state transition to Active
    this.Raise(new Unit());
  }
}
\end{lstlisting}
\vspace{-2mm}
\caption{Timers in Azure Storage vNext are modeled as a nondeterministic \psharp machines.}
\label{fig:timer}
%\vspace{-2mm}
\end{figure}

>>>>

In the following subsections, we will use the Azure Storage vNext case study as a running example of how to model a typical distributed system using \psharp. In principle, this modeling methodology is not specific to \psharp but can be used in combination with any systematic testing tool. We decided to use \psharp as it is a mature tool that provides a lot of modeling power via its \csharp language extensions and has an embedded systematic concurrency testing engine inside its runtime.

@@

  void ProcessTickEvent()
  {
    // Nondeterministic boolean choice controlled by P#
    if (this.Nondet())
      // sends a timer tick event to the owner machine
      this.Send(this.Owner, new TimerTickEvent());
    // triggers state transition to Active
    this.Raise(new Unit());
  }
}
\end{lstlisting}
\vspace{-2mm}
\caption{Timers in Azure Storage vNext are modeled as nondeterministic \psharp machines.}
\label{fig:timer}
%\vspace{-2mm}
\end{figure}
